Model LF

### 2022-11-09 Estimation.Rmd

>>>>

### pconk_ds

```{r}
"C_2*TSLAG(LOG(pconk_ds),1) + C_3*TSLAG(LOG(yd1_hk_ds),1) + C_4*LOG(TSLAG(yd2a_hk_ds,1) + TSLAG(yd2b_hk,1)) + C_5*TSLAG(LOG(fnw_hk),2) + C_6*TSDELTALOG(TSLAG(pconk_ds,2)) + C_7*TSDELTALOG(TSLAG(pconk_ds,3)) + C_8*TSDELTALOG(yd1_hk_ds)  + C_9*TSDELTALOG(yd2a_hk_ds + yd2b_hk) + C_10*d_2008q4 + C_11*d_2018q2 + C_12*d_2020q1 + C_13* time"
```

```{r}
reg_prod_start=dynlm(TSDELTALOG(pconk_ds) ~ 0+ TSLAG(log(pconk_ds),1) + TSLAG(log(yd1_hk_ds),1) + log(TSLAG(yd2a_hk_ds,1) + TSLAG(yd2b_hk,1)) + TSLAG(log(fnw_hk),2) + TSDELTALOG(TSLAG(pconk_ds,2)) + TSDELTALOG(TSLAG(pconk_ds,3)) + TSDELTALOG(yd1_hk_ds)  + TSDELTALOG(yd2a_hk_ds + yd2b_hk) + d_2008q4 + d_2018q2 + d_2020q1 + trend(pconk_ds))
